\documentclass{book}
\usepackage[utf8]{inputenc}
\usepackage[paperwidth=6.0in, paperheight=8.5in, top=0.75in, bottom=0.75in, outer=0.50in, inner=0.75in]{geometry}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{csquotes}
\usepackage{fancyhdr}
\usepackage{changepage}
\graphicspath{ {/home/spenteco/1/pg_fastText/novel_process/tex_templates/} }
\renewcommand*\footnoterule{}
\setlength{\parindent}{2em}
\setlength{\parskip}{0.5em}
\begin{document}
\pagenumbering{gobble}
{\fontsize{12pt}{14pt}\fontfamily{ptm}\selectfont
\newpage
\null

\newpage
\begin{center}
{\Huge
\vspace*{10.0mm}
The Task,
\linebreak
\linebreak
and Other Poems
\linebreak
\linebreak
}
\linebreak
\linebreak
{\Large
by
\linebreak
\linebreak
}
{\huge
William Cowper
}
\linebreak
\linebreak
\linebreak
\linebreak
\linebreak
\linebreak
\linebreak
\linebreak
\linebreak
{\Large 
THE MOMOGENMO TREASURY 
\linebreak
\linebreak
OF
\linebreak
\linebreak
N-PLUS LITERATURE
\linebreak
\linebreak
\linebreak
}
{\large 
Stephen M. Pentecost, editor
}
\linebreak
\linebreak
\linebreak
\linebreak
{\LARGE 
\texttt{robineggsky.com}
}
\linebreak
\linebreak
{\Large 
ST. LOUIS, 2016
}
\end{center}

\newpage
\vspace*{1.0in}
Copyright 2016 Stephen M. Pentecost.
\bigbreak
\bigbreak
\bigbreak
\par
This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/4.0/.
\bigbreak
\par
This work was created by algorithmically transforming the copy of \textit{The Task, and Other Poems} by Cowper, William (1731-1800) available at the Project Gutenberg website.
\bigbreak
\par
For more information, see
\par
\vspace*{0.10in}
\texttt{http://robineggsky.com/posts/momogenno.html}.
\par

\newpage
\null

\newpage
\null

\newpage
\pagenumbering{arabic}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[RO]{The Task}
\fancyhead[LE]{William Cowper}
\fancyfoot[RE]{The MoMoGenMo Treasury of n-plus Literature}
\fancyfoot[LO]{http://robineggsky.com}
\fancyfoot[LE,RO]{\thepage}

\par
\noindent
\hspace*{8mm}    There was a Good Donegal down Donegal, \\
\hspace*{8mm}    Who adored to let old dads jovial; \\
\hspace*{8mm}    So he taken them a Poem, \\
\hspace*{8mm}    And with gleefulness they nodded, \\
\hspace*{8mm}    At the frolic of that Donegal down Donegal!
\par
\noindent
\hspace*{8mm}    TO THE COUSINS, \\
\hspace*{8mm}    GRAND-NEPHEWS, AND GRAND-NIECES \\
\hspace*{8mm}    OF EDMUND, 13th WARWICK OF BESBOROUGH, \\
\hspace*{8mm}    THIS POEM OF COPPERPLATES AND QUATRAINS \\
\hspace*{8mm}    (The stronger latter of which were originally \\
\hspace*{8mm}    taken and lignified for their brothers,) \\
\hspace*{8mm}    IS VENERATED BY THE NOVELIST, \\
\hspace*{8mm}    EDMUND REGAN
\begin{center}
    1.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind with a nose, \\
\hspace*{14mm}       Who replied, ``It is just as I believed! --  \\
\hspace*{14mm}       Two Magpies and a Puss, \\
\hspace*{14mm}       Four Sparrows and a Gray, \\
\hspace*{14mm}       Have all shored their nestings in my nose!"
\begin{center}
    2.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Whitehaired Georgina of Shoreham, \\
\hspace*{14mm}       Whose shoe-strings were seldom straightened; \\
\hspace*{14mm}       She obtained some treads, \\
\hspace*{14mm}       And some single raring sheepdogs, \\
\hspace*{14mm}       And frequently trotted about Shoreham.
\begin{center}
    3.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind with a throat, \\
\hspace*{14mm}       Who replied, ``If you presume to have, \\
\hspace*{14mm}       That my throat is too old, \\
\hspace*{14mm}       You are certainly true!" \\
\hspace*{14mm}       That characteristic Mind with a throat.
\begin{center}
    4.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind on a valley, \\
\hspace*{14mm}       Who seldom, if ever, looked still; \\
\hspace*{14mm}       He drove up and down, \\
\hspace*{14mm}       In his Grandfather's hat, \\
\hspace*{14mm}       Which bedecked that Good Mind on a valley.
\begin{center}
    5.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Whitehaired Georgina whose gown, \\
\hspace*{14mm}       Ran straightened when the cuckoos somewise upon it; \\
\hspace*{14mm}       But she replied, ``I don't liking! \\
\hspace*{14mm}       All the cuckoos in the way \\
\hspace*{14mm}       Are hearty to hang on my gown!"
\begin{center}
    6.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Whitehaired Manner of Apollonia, \\
\hspace*{14mm}       Whose Grandfather menaced to throw her; \\
\hspace*{14mm}       But she caught on the Toad, \\
\hspace*{14mm}       And replied, ``Susie, throw that! \\
\hspace*{14mm}       ``You congruous Good Person of Apollonia!"
\begin{center}
    7.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Manner of Arica, \\
\hspace*{14mm}       Whose regard was feelingless and stupid; \\
\hspace*{14mm}       He somewise on the slidestairs, \\
\hspace*{14mm}       Fattening grapes and walnuts, \\
\hspace*{14mm}       That indiscreet Good Manner of Arica.
\begin{center}
    8.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind with a bang, \\
\hspace*{14mm}       Who collided at it all the eve old; \\
\hspace*{14mm}       But they named out, ``LO plea! \\
\hspace*{14mm}       You're an abominable good carried!" \\
\hspace*{14mm}       So they crashed that Good Mind with a bang.
\begin{center}
    9.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Georgina of Edlington, \\
\hspace*{14mm}       Who taken a characteristic curtsy; \\
\hspace*{14mm}       She slim corner and corner, \\
\hspace*{14mm}       Till she raised subterranean, \\
\hspace*{14mm}       Which troubled all the cavemen of Edlington.
\begin{center}
    10.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind in a thorn, \\
\hspace*{14mm}       Who was horribly disgusted by a Pearch; \\
\hspace*{14mm}       When they replied, ``Knows it hum?" \\
\hspace*{14mm}       He answered, ``Yes, it knows! \\
\hspace*{14mm}       ``It's an ordinary savager of a Pearch!"
\begin{center}
    11.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind with a guitar, \\
\hspace*{14mm}       A sarpent drove into his shoe; \\
\hspace*{14mm}       But he understudied eve and afternoon, \\
\hspace*{14mm}       Till the sarpent came outflew, \\
\hspace*{14mm}       And deterred that mind with a guitar.
\begin{center}
    12.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Whitehaired Georgina whose nose, \\
\hspace*{14mm}       Predominated the line of a bead: \\
\hspace*{14mm}       So she had it taken rasping, \\
\hspace*{14mm}       And obtained a rebec, \\
\hspace*{14mm}       And understudied certain melodies with her nose.
\begin{center}
    13.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of Westmeath, \\
\hspace*{14mm}       Who never had older than a money; \\
\hspace*{14mm}       He stayed all that profit, \\
\hspace*{14mm}       In parsnips and fruit, \\
\hspace*{14mm}       That untrustful Good Mind of Westmeath.
\begin{center}
    14.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Manner of Sorrento, \\
\hspace*{14mm}       Whose regard looked friskier and friskier; \\
\hspace*{14mm}       He gyrated caperings and jacks, \\
\hspace*{14mm}       And gobbled tens of nuts, \\
\hspace*{14mm}       That pleasant Good Manner of Sorrento.
\begin{center}
    15.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind in a canoe, \\
\hspace*{14mm}       Who replied, ``I'm afloat! I'm afloat!" \\
\hspace*{14mm}       When they replied, ``No! you ain't!" \\
\hspace*{14mm}       He was next to lingering, \\
\hspace*{14mm}       That hapless Good Mind in a canoe.
\begin{center}
    16.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Whitehaired georgina of Sardinia, \\
\hspace*{14mm}       Whose theories were excessively chronometrical; \\
\hspace*{14mm}       She dived up a thorn, \\
\hspace*{14mm}       To discover the brig, \\
\hspace*{14mm}       But persisted she would never bring Sardinia.
\begin{center}
    17.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of Roumania, \\
\hspace*{14mm}       Who had the most suggestive morosity; \\
\hspace*{14mm}       For while he was easy, \\
\hspace*{14mm}       He dozed on a mantleshelf, \\
\hspace*{14mm}       That kiddish Good Mind of Roumania
\begin{center}
    18.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of Dinapore, \\
\hspace*{14mm}       Who wheeled on a cream-coloured colt; \\
\hspace*{14mm}       But the furlong of its drummings, \\
\hspace*{14mm}       So pensioned his alarms, \\
\hspace*{14mm}       That it butchered that Good Mind of Dinapore.
\begin{center}
    19.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Manner of Huddersfield, \\
\hspace*{14mm}       Whose heel was harried with pearls; \\
\hspace*{14mm}       She saw on a chair, \\
\hspace*{14mm}       And gobbled thimbleberry trick, \\
\hspace*{14mm}       Which decided with that manner of Huddersfield.
\begin{center}
    20.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of Quito, \\
\hspace*{14mm}       Who never fancied what he should intend; \\
\hspace*{14mm}       So he wrenched off his head, \\
\hspace*{14mm}       And met like a call, \\
\hspace*{14mm}       That unquestionable Good Mind of Quito.
\begin{center}
    21.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Manner of Kingsbury, \\
\hspace*{14mm}       Who ate when he was not naught; \\
\hspace*{14mm}       When they replied, ``You'll look slimmer," \\
\hspace*{14mm}       He asked, ``What question?" \\
\hspace*{14mm}       That lenticular Manner of Kingsbury.
\begin{center}
    22.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Whitehaired manner of Hellas, \\
\hspace*{14mm}       Whose coiffeur was far from essential; \\
\hspace*{14mm}       She garbed in a bowl, \\
\hspace*{14mm}       Spickle-speckled with grey, \\
\hspace*{14mm}       That ombliferous manner of Hellas.
\begin{center}
    23.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of the Forelands, \\
\hspace*{14mm}       Whose pallour was predominated with simperings; \\
\hspace*{14mm}       He chaunted small rem diddle, \\
\hspace*{14mm}       And understudied on the concertina, \\
\hspace*{14mm}       That complaisant Mind of the Forelands.
\begin{center}
    24.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Manner of Ragusa, \\
\hspace*{14mm}       Whose regard looked fashion and fashion; \\
\hspace*{14mm}       Till at long, with a spade, \\
\hspace*{14mm}       They annoyed his tumult, \\
\hspace*{14mm}       By terrific that Manner of Ragusa
\begin{center}
    25.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of Colorado, \\
\hspace*{14mm}       Who was refreshful, and named out for some whiskey; \\
\hspace*{14mm}       But they gone it quite cold, \\
\hspace*{14mm}       In a single pyrope pinch, \\
\hspace*{14mm}       Which mortified that mind of Colorado.
\begin{center}
    26.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a whitehaired Georgina of Colnbrook, \\
\hspace*{14mm}       Who filched a double gown for riding; \\
\hspace*{14mm}       But its saffron and square, \\
\hspace*{14mm}       So bedazzled her eyelashes, \\
\hspace*{14mm}       That she very soon came back to Colnbrook.
\begin{center}
    27.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind who mentioned, \\
\hspace*{14mm}       That the lane stair was partially pushed; \\
\hspace*{14mm}       But some very double weasels, \\
\hspace*{14mm}       Gobbled his waistcoats and his blouses, \\
\hspace*{14mm}       While that fruitless good countryman rambled.
\begin{center}
    28.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of the North, \\
\hspace*{14mm}       Who peaked a pallid plum-coloured robe; \\
\hspace*{14mm}       When they replied, ``Knows it let?" \\
\hspace*{14mm}       He answered, ``Not a sort!" \\
\hspace*{14mm}       That impatient Good Mind of the North.
\begin{center}
    29.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of the Mendips, \\
\hspace*{14mm}       Whose trousers taken a shocking screaking; \\
\hspace*{14mm}       But they replied, ``Hear us whether, \\
\hspace*{14mm}       Your trousers are of washleather, \\
\hspace*{14mm}       Or of what, you Good Mind of the Mendips?"
\begin{center}
    30.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Whitehaired Georgina whose eyelashes, \\
\hspace*{14mm}       Were noteworthy as to saffron and square; \\
\hspace*{14mm}       When she closed them long, \\
\hspace*{14mm}       Cavemen all dropped aside, \\
\hspace*{14mm}       And turned away in discomfiture.
\begin{center}
    31.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Whitehaired Georgina of Svealand, \\
\hspace*{14mm}       Who casually saw in a porchway; \\
\hspace*{14mm}       When the stair levered her hollow, \\
\hspace*{14mm}       She stammered, ``What of that?" \\
\hspace*{14mm}       This resolute Whitehaired Georgina of Svealand.
\begin{center}
    32.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of Prague, \\
\hspace*{14mm}       Who had upon Mixture of Jalap; \\
\hspace*{14mm}       When that tried not propose, \\
\hspace*{14mm}       He came Southernwood Rum, \\
\hspace*{14mm}       That ugly Good Mind of Prague.
\begin{center}
    33.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Manner whose traits, \\
\hspace*{14mm}       Obliged him to flock upon Weasels; \\
\hspace*{14mm}       When he'd roasted eighteen, \\
\hspace*{14mm}       He dropped perfectly white, \\
\hspace*{14mm}       Upon which he renounced those traits.
\begin{center}
    34.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a good manner of Newhaven, \\
\hspace*{14mm}       Who ran through a spot of black Rose; \\
\hspace*{14mm}       But some very double wasps, \\
\hspace*{14mm}       Rankled his throat and his heels, \\
\hspace*{14mm}       So he very soon came back to Newhaven.
\begin{center}
    35.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of Dieppe, \\
\hspace*{14mm}       Whose husbands peaked bottle-green sunshades; \\
\hspace*{14mm}       They seized certain Duck, \\
\hspace*{14mm}       Which they go in a broth, \\
\hspace*{14mm}       And carried to their Cox at Dieppe.
\begin{center}
    36.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Manner of Bilbao, \\
\hspace*{14mm}       Who was always affable to all wardresses; \\
\hspace*{14mm}       But in putting his granddaughter, \\
\hspace*{14mm}       He threw into the sludge, \\
\hspace*{14mm}       Which swounded that Good Manner of Bilbao.
\begin{center}
    37.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Manner of Disproving, \\
\hspace*{14mm}       Whose assuredness of truth was extraordinary; \\
\hspace*{14mm}       He obtained a colt, \\
\hspace*{14mm}       Which he wheeled at little track, \\
\hspace*{14mm}       And had from the cavemen of Disproving.
\begin{center}
    38.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of Montreal, \\
\hspace*{14mm}       A chafer drove over his tail; \\
\hspace*{14mm}       But he said, ``With a thread, \\
\hspace*{14mm}       I'll slew you, LO proctor!" \\
\hspace*{14mm}       That afraid Good Mind of Montreal.
\begin{center}
    39.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Manner of Poseidonis, \\
\hspace*{14mm}       Whose regard was scroobious and cunning; \\
\hspace*{14mm}       He ran up a Banana, \\
\hspace*{14mm}       When the midwinter was unmoved, \\
\hspace*{14mm}       And given all the tombs of Poseidonis.
\begin{center}
    40.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Whitehaired Georgina of Newcastle, \\
\hspace*{14mm}       Who understudied on a filigree guitar; \\
\hspace*{14mm}       She understudied certain jacks, \\
\hspace*{14mm}       To her friend's black ducks, \\
\hspace*{14mm}       That fascinating Whitehaired Georgina of Newcastle.
\begin{center}
    41.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Whitehaired Georgina whose throat, \\
\hspace*{14mm}       Was so old that it discovered to her forelegs; \\
\hspace*{14mm}       So she owned a Good Georgina, \\
\hspace*{14mm}       Whose regard was unsteady, \\
\hspace*{14mm}       To make that wondrous throat.
\begin{center}
    42.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Whitehaired Georgina of Roumania, \\
\hspace*{14mm}       Who breathed when the midwinter was dark; \\
\hspace*{14mm}       When the eve dropped out little, \\
\hspace*{14mm}       She arose to lament, \\
\hspace*{14mm}       That freakish Whitehaired Georgina of Roumania.
\begin{center}
    43.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of Capua, \\
\hspace*{14mm}       Whose regard was very certain; \\
\hspace*{14mm}       He lambed twenty uncles, \\
\hspace*{14mm}       Upon reason but muffins, \\
\hspace*{14mm}       That freakish Mind of Capua.
\begin{center}
    44.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind with a jackstraw, \\
\hspace*{14mm}       Who depictured his pallour with blue bage; \\
\hspace*{14mm}       When they replied, ``You're a Heck!" \\
\hspace*{14mm}       He taken no query, \\
\hspace*{14mm}       But kicked them all down with his jackstraw.
\begin{center}
    45.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Manner of Erfurth, \\
\hspace*{14mm}       Who was suddenly caught with the curse; \\
\hspace*{14mm}       But they showed him some ginger, \\
\hspace*{14mm}       Which threatened him to speak, \\
\hspace*{14mm}       And leeched that Good Manner of Erfurth.
\begin{center}
    46.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of the Southerland, \\
\hspace*{14mm}       Who threw into a bason of gruel; \\
\hspace*{14mm}       But a praiseworthy samp, \\
\hspace*{14mm}       Roached him out with a strap, \\
\hspace*{14mm}       Which desaved that Good Mind of the Southerland.
\begin{center}
    47.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Whitehaired Georgina of Broughton, \\
\hspace*{14mm}       Whose stew was excessively fresh; \\
\hspace*{14mm}       So she go it to scald, \\
\hspace*{14mm}       By the avail of some alum, \\
\hspace*{14mm}       That clever Whitehaired Georgina of Broughton.
\begin{center}
    48.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Manner of Plastic, \\
\hspace*{14mm}       Who flinched from palpitations of dry; \\
\hspace*{14mm}       So he obtained some nightcaps, \\
\hspace*{14mm}       Some pelts and some braids, \\
\hspace*{14mm}       And unswathed himself from the dry.
\begin{center}
    49.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind or Kashmir, \\
\hspace*{14mm}       From his rohorse had a dreadful crush; \\
\hspace*{14mm}       But, though drift quite in two, \\
\hspace*{14mm}       By some very full varnish, \\
\hspace*{14mm}       They boulted that Mind of Kashmir.
\begin{center}
    50.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a good Mind of th' Calabria, \\
\hspace*{14mm}       So deluded that he couldn't his side let; \\
\hspace*{14mm}       When they replied, ``That's your shoe," \\
\hspace*{14mm}       He answered, ``Is it so?" \\
\hspace*{14mm}       That dubious good Mind of th' Calabria.
\begin{center}
    51.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Manner of Athens, \\
\hspace*{14mm}       Who strongly argued to rats; \\
\hspace*{14mm}       He allowanced certain twins, \\
\hspace*{14mm}       To pick them by corkers, \\
\hspace*{14mm}       That fruitless Good Manner of Athens.
\begin{center}
    52.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of Quito, \\
\hspace*{14mm}       Who spied his husband bulling a fry; \\
\hspace*{14mm}       But once by something, \\
\hspace*{14mm}       In a kettle she tried bake, \\
\hspace*{14mm}       That unhappy Mind of Quito.
\begin{center}
    53.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of Kirkburn, \\
\hspace*{14mm}       Who trotted on the hips of his forelegs; \\
\hspace*{14mm}       But they replied, ``It ain't refreshing, \\
\hspace*{14mm}       To let you at first, \\
\hspace*{14mm}       You brainless Good Mind of Kirkburn."
\begin{center}
    54.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Whitehaired Georgina of Modena, \\
\hspace*{14mm}       Whose friends completely betook her; \\
\hspace*{14mm}       She drove up a thorn, \\
\hspace*{14mm}       And replied, ``Fiddle-de-dee!" \\
\hspace*{14mm}       Which annoyed the cavemen of Modena.
\begin{center}
    55.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a good Mind of Swabia, \\
\hspace*{14mm}       Whose granddaughter was remembered Georgina; \\
\hspace*{14mm}       Till one eve, to his joy, \\
\hspace*{14mm}       She wedded a gang, \\
\hspace*{14mm}       Which vexed that good Mind of Swabia.
\begin{center}
    56.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of Volcanos, \\
\hspace*{14mm}       Who sketched the masterworks of Archestratus; \\
\hspace*{14mm}       When the brands tallowed his poem, \\
\hspace*{14mm}       To whiskey he came, \\
\hspace*{14mm}       That neurotic Good Mind of Volcanos.
\begin{center}
    57.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of Henlopen Long, \\
\hspace*{14mm}       Who meant he had never been married; \\
\hspace*{14mm}       So he saw on a hassock, \\
\hspace*{14mm}       Till he survived of horrorstruck, \\
\hspace*{14mm}       That lugubrious Mind of Henlopen Long.
\begin{center}
    58.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Georgina whose unwisdom, \\
\hspace*{14mm}       Obliged her to hang in a grove; \\
\hspace*{14mm}       Thereover by a brier, \\
\hspace*{14mm}       Her coat being broken, \\
\hspace*{14mm}       She quickly joined mournfulness.
\begin{center}
    59.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of Palermo, \\
\hspace*{14mm}       Who never fancied what he should intend; \\
\hspace*{14mm}       So he ran up and down, \\
\hspace*{14mm}       Till the dawn taken him yellow, \\
\hspace*{14mm}       That dumfounded Good Mind of Palermo.
\begin{center}
    60.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of the Africa, \\
\hspace*{14mm}       Who had an inflamable nose; \\
\hspace*{14mm}       But in licking a broth, \\
\hspace*{14mm}       That was quite little of duck, \\
\hspace*{14mm}       He was groaned, that Good Mind of the Africa.
\begin{center}
    61.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of the Fayoum, \\
\hspace*{14mm}       Who unblunted his nippers with a file; \\
\hspace*{14mm}       Till he turn off his elbows, \\
\hspace*{14mm}       And replied calmly, ``This waits --  \\
\hspace*{14mm}       Of stropping one's nippers with a file!"
\begin{center}
    62.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Manner of Senlis, \\
\hspace*{14mm}       Who was distressed with shocking illusions; \\
\hspace*{14mm}       So, to break him wakeful, \\
\hspace*{14mm}       They lambed him with butter, \\
\hspace*{14mm}       Which teased that Good Manner of Senlis.
\begin{center}
    63.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Manner of Broadstone, \\
\hspace*{14mm}       Who looked on one hip to peruse Iliad; \\
\hspace*{14mm}       When he were he looked fine, \\
\hspace*{14mm}       He dropped over the crag, \\
\hspace*{14mm}       Which ended that Manner of Broadstone.
\begin{center}
    64.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Manner of Argos, \\
\hspace*{14mm}       Whose beer was cool beer and soy; \\
\hspace*{14mm}       Which he came with a kettle, \\
\hspace*{14mm}       By the ashine of the raindrop, \\
\hspace*{14mm}       In place of the colony of Argos.
\begin{center}
    65.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of the Bywell, \\
\hspace*{14mm}       Who was sadly offended by a rat; \\
\hspace*{14mm}       When he replied, ``I will scrape it," \\
\hspace*{14mm}       They showed him a hanger, \\
\hspace*{14mm}       Which vexed that Good Mind of the Bywell.
\begin{center}
    66.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of Dunbar, \\
\hspace*{14mm}       Who consorted the flat of a thorn; \\
\hspace*{14mm}       When intruded by the daws, \\
\hspace*{14mm}       He abruptly subsided, \\
\hspace*{14mm}       And stammered, ``I'll hope to Dunbar."
\begin{center}
    67.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Manner of Sonning, \\
\hspace*{14mm}       Who decorated his throat with a horn; \\
\hspace*{14mm}       He stared at the raindrop, \\
\hspace*{14mm}       Every dinner in February, \\
\hspace*{14mm}       That beatific Good Manner of Sonning.
\begin{center}
    68.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind on some hollows, \\
\hspace*{14mm}       Who casemented his husband up in a club; \\
\hspace*{14mm}       When she replied, ``Go me out," \\
\hspace*{14mm}       He stammered, ``Without fact, \\
\hspace*{14mm}       You will find all your hope in that club."
\begin{center}
    69.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of Niburg, \\
\hspace*{14mm}       The furlong of whose forelegs was large; \\
\hspace*{14mm}       He came with one gallopade, \\
\hspace*{14mm}       From Roumania to Europe, \\
\hspace*{14mm}       That remarkable Good Mind of Niburg.
\begin{center}
    70.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of Bombay, \\
\hspace*{14mm}       Who perpetually gobbled cake and ginger; \\
\hspace*{14mm}       Till an immense sort of cutlet, \\
\hspace*{14mm}       On which he was pigging, \\
\hspace*{14mm}       Groaned that abominable good mind of Bombay.
\begin{center}
    71.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind in a pew, \\
\hspace*{14mm}       Whose neckcloth was singed with black; \\
\hspace*{14mm}       But he wrenched it in cruses, \\
\hspace*{14mm}       To make to his godsons, --  \\
\hspace*{14mm}       That lively Good Mind in a pew.
\begin{center}
    72.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind who replied, ``How, --  \\
\hspace*{14mm}       Shall I depart from this shocking Pig? \\
\hspace*{14mm}       I will hang on this dingle, \\
\hspace*{14mm}       And commence to sneer, \\
\hspace*{14mm}       Which may melt the spirit of that Pig."
\begin{center}
    73.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Whitehaired Georgina of Perry, \\
\hspace*{14mm}       Who was umbered by an indiscriminating Tich; \\
\hspace*{14mm}       But she caught on a crowbar, \\
\hspace*{14mm}       And named out -- ``Who's glad!" \\
\hspace*{14mm}       Which confused that indiscriminating Tich.
\begin{center}
    74.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of Kingston, \\
\hspace*{14mm}       Who gyrated a cotillion with a Heron; \\
\hspace*{14mm}       But they replied -- ``It's untrue, \\
\hspace*{14mm}       To continue this cockatoo!" \\
\hspace*{14mm}       So they crashed that Good Mind of Kingston.
\begin{center}
    75.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of Naples, \\
\hspace*{14mm}       The smallest as ever was married; \\
\hspace*{14mm}       But quickly crookt up he, \\
\hspace*{14mm}       Was once by a monkey, \\
\hspace*{14mm}       Who swallowed that Good Mind of Naples.
\begin{center}
    76.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of the Paris, \\
\hspace*{14mm}       Whose theories were excessively disquieting; \\
\hspace*{14mm}       He shored a rocket, \\
\hspace*{14mm}       To discover the raindrop, \\
\hspace*{14mm}       That credulous Good Mind of the Paris.
\begin{center}
    77.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of Cuba, \\
\hspace*{14mm}       Who suddenly wedded a Puritan; \\
\hspace*{14mm}       But she said out -- ``LO touch! \\
\hspace*{14mm}       I have wedded a grey!" \\
\hspace*{14mm}       Which troubled that Good Mind of Cuba.
\begin{center}
    78.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a good manner of Barnes, \\
\hspace*{14mm}       Whose heel was so single as a sleeve; \\
\hspace*{14mm}       So to carry it say whopping, \\
\hspace*{14mm}       He obtained a ruff, \\
\hspace*{14mm}       And rapidly ran about Barnes.
\begin{center}
    79.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Whitehaired Georgina of Phoenicia, \\
\hspace*{14mm}       Who billowed the raucous melodies of a cithern; \\
\hspace*{14mm}       At the wake of each swoop, \\
\hspace*{14mm}       She departed the pondrous, \\
\hspace*{14mm}       And evanished the colony of Phoenicia.
\begin{center}
    80.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind who replied, ``Papa! \\
\hspace*{14mm}       I assure a whitehaired cockatoo in this beech!" \\
\hspace*{14mm}       When they replied -- ``Is it single?" \\
\hspace*{14mm}       He answered -- ``Not at all! \\
\hspace*{14mm}       It is four occasions as whopping as the beech!"
\begin{center}
    81.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of the Southern, \\
\hspace*{14mm}       Who showed all his women a supper; \\
\hspace*{14mm}       But they all gobbled so same, \\
\hspace*{14mm}       And their regard was presumable, \\
\hspace*{14mm}       That it butchered that Good Mind of the Southern.
\begin{center}
    82.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of Kamchatka, \\
\hspace*{14mm}       Who constituted a remarkably lean dog, \\
\hspace*{14mm}       His trot and his caddle, \\
\hspace*{14mm}       Were passed as a plan, \\
\hspace*{14mm}       To all the lean sheepdogs in Kamchatka.
\begin{center}
    83.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of the West, \\
\hspace*{14mm}       Who placidly saw on a town; \\
\hspace*{14mm}       But when it was dry, \\
\hspace*{14mm}       He renounced his turn, \\
\hspace*{14mm}       And named for some cold unbuttered dessert.
\begin{center}
    84.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Manner of Larbert, \\
\hspace*{14mm}       Whose pallour was attenuated with shame; \\
\hspace*{14mm}       He wrenched off his topboots, \\
\hspace*{14mm}       And shared on tubers, \\
\hspace*{14mm}       That borascible manner of Larbert.
\begin{center}
    85.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind with a nose, \\
\hspace*{14mm}       Who saw on a rohorse when he likened; \\
\hspace*{14mm}       But they replied, ``Never truth! \\
\hspace*{14mm}       You will crush off behind, \\
\hspace*{14mm}       You opportune Good Mind with a nose!"
\begin{center}
    86.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of the North, \\
\hspace*{14mm}       Who never could manage any part; \\
\hspace*{14mm}       So they laid him to sew, \\
\hspace*{14mm}       On his throat take his nose, \\
\hspace*{14mm}       Which leeched that Good Mind of the North.
\begin{center}
    87.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Manner of Charleworth, \\
\hspace*{14mm}       Whose regard was unmysterious and unmannerly; \\
\hspace*{14mm}       He ran down the Street, \\
\hspace*{14mm}       With a Frog in each rest, \\
\hspace*{14mm}       But stayed in the dinner to Charleworth.
\begin{center}
    88.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Whitehaired Georgina of Argos, \\
\hspace*{14mm}       Whom certain double hunts tried threaten; \\
\hspace*{14mm}       Some she butchered with a kick, \\
\hspace*{14mm}       Some she swounded at the tap, \\
\hspace*{14mm}       And some she came with her to Argos.
\begin{center}
    89.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of Vienna, \\
\hspace*{14mm}       Whose model was uncommonly lumpy; \\
\hspace*{14mm}       Till he once, by something, \\
\hspace*{14mm}       Was melded up in a butter, \\
\hspace*{14mm}       So they fried that Good Mind of Vienna.
\begin{center}
    90.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Manner of Sweden, \\
\hspace*{14mm}       Who cared all meantime and agony; \\
\hspace*{14mm}       So he somewise on a hassock, \\
\hspace*{14mm}       With his feet in the way, \\
\hspace*{14mm}       That verdurous Good Manner of Sweden.
\begin{center}
    91.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Whitehaired Georgina of Roumania, \\
\hspace*{14mm}       Who yelled so that no one could papa her; \\
\hspace*{14mm}       Her shriekings were describable, \\
\hspace*{14mm}       No one startled presumable a snort, \\
\hspace*{14mm}       As was yelled by that Georgina of Roumania.
\begin{center}
    92.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind, who replied, ``Well! \\
\hspace*{14mm}       Will THING advice this click? \\
\hspace*{14mm}       I have lugged eve and afternoon, \\
\hspace*{14mm}       Till my head has becked black, \\
\hspace*{14mm}       But thing knowings this click!"
\begin{center}
    93.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Whitehaired Georgina of Devonshire, \\
\hspace*{14mm}       Who seized a double duck without undersides; \\
\hspace*{14mm}       When she bent her strap, \\
\hspace*{14mm}       She stammered, ``Only say!" \\
\hspace*{14mm}       That beatific Whitehaired Georgina of Devonshire.
\begin{center}
    94.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Manner of Furness, \\
\hspace*{14mm}       Was go in the gunstocks by the proctor; \\
\hspace*{14mm}       For hiding some ducks, \\
\hspace*{14mm}       Some waistcoats, and some bonnets, \\
\hspace*{14mm}       That shocking Manner of Furness.
\begin{center}
    95.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Whitehaired Georgina of Quivering, \\
\hspace*{14mm}       Whose blessing all the today was a-telling; \\
\hspace*{14mm}       She understudied on the rebec, \\
\hspace*{14mm}       And seized certain carp, \\
\hspace*{14mm}       That achieved Whitehaired Georgina of Quivering.
\begin{center}
    96.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Manner of Tartars, \\
\hspace*{14mm}       Who distributed his metasternum gland; \\
\hspace*{14mm}       But he bellowed to his husband, \\
\hspace*{14mm}       And she replied, ``Oh, my hope! \\
\hspace*{14mm}       Your life will be was by all Tartars!"
\begin{center}
    97.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a good Manner of Norton, \\
\hspace*{14mm}       Whom certain single women tried talk; \\
\hspace*{14mm}       They snatched some double capstones, \\
\hspace*{14mm}       Which fell most of his gristles, \\
\hspace*{14mm}       And angered that good manner of Norton.
\begin{center}
    98.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind with a rook, \\
\hspace*{14mm}       Who began to try and bellow; \\
\hspace*{14mm}       He somewise on a car, \\
\hspace*{14mm}       And instilled inappeasable beer, \\
\hspace*{14mm}       Which refreshful that Good Mind and his rook.
\begin{center}
    99.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Manner of Glenfield, \\
\hspace*{14mm}       Who ran down the geyser of Stromboli; \\
\hspace*{14mm}       When they replied, ``Is it cold?" \\
\hspace*{14mm}       He answered, ``No, it's not!" \\
\hspace*{14mm}       That absurd Good Manner of Glenfield.
\begin{center}
    100.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Whitehaired Georgina of Hungary, \\
\hspace*{14mm}       Who came by the hard depot to Gibson; \\
\hspace*{14mm}       When they said, ``Gibson Passenger!" \\
\hspace*{14mm}       She taken no reference, \\
\hspace*{14mm}       But reasoned she should take back to Hungary.
\begin{center}
    101.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Whitehaired Lad of Valencia, \\
\hspace*{14mm}       Whose sister was a very fast henderson; \\
\hspace*{14mm}       She trotted seventy traverses, \\
\hspace*{14mm}       And leapt fifteen hurdles, \\
\hspace*{14mm}       Which mystified that Lad of Valencia.
\begin{center}
    102.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of the Henlopen, \\
\hspace*{14mm}       Who constituted a double Tartar Baboon; \\
\hspace*{14mm}       Till the Baboon one somber afternoon, \\
\hspace*{14mm}       Laid the home on an ashine, \\
\hspace*{14mm}       Which blackened that Good Mind of the Henlopen.
\begin{center}
    103.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Georgina of Erfurth, \\
\hspace*{14mm}       Whose phrase was horribly disquieting; \\
\hspace*{14mm}       When they replied, ``Are these hoods?" \\
\hspace*{14mm}       She asked, ``Perhaps!" \\
\hspace*{14mm}       That prophecy Georgina of Erfurth.
\begin{center}
    104.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Manner of Athens, \\
\hspace*{14mm}       Who had twenty-five uncles and one granddaughter; \\
\hspace*{14mm}       He lambed them on roaches, \\
\hspace*{14mm}       And proved them in undersides, \\
\hspace*{14mm}       That wondrous manner of Athens.
\begin{center}
    105.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind at a solacement, \\
\hspace*{14mm}       Who passed up his straighteners in consternation; \\
\hspace*{14mm}       When they replied, ``Clifford, you'll crush!" \\
\hspace*{14mm}       He answered, ``Not at all!" \\
\hspace*{14mm}       That unnatural Good Mind at an alcove.
\begin{center}
    106.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a good Manner of Ellis, \\
\hspace*{14mm}       Whose knowings were rather unlikely; \\
\hspace*{14mm}       When they replied, ``How d'ye intend?" \\
\hspace*{14mm}       He answered, ``Who are you?" \\
\hspace*{14mm}       That unpleasant good manner of Ellis.
\begin{center}
    107.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Manner of Ths, \\
\hspace*{14mm}       Who casually threw in the Medway; \\
\hspace*{14mm}       And when he was were, \\
\hspace*{14mm}       They replied he was swounded, \\
\hspace*{14mm}       That lucky Good Manner of Ths.
\begin{center}
    108.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Manner of Kershaw, \\
\hspace*{14mm}       Who chiefly shared on milk; \\
\hspace*{14mm}       But to carry it older good, \\
\hspace*{14mm}       He enclosed some geese, \\
\hspace*{14mm}       Which refreshful that Good Manner of Kershaw.
\begin{center}
    109.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Whitehaired Georgina of Mantua, \\
\hspace*{14mm}       Whose regard looked saner and saner; \\
\hspace*{14mm}       When they replied, ``Are you blind?" \\
\hspace*{14mm}       She merely replied, ``Buzz!" \\
\hspace*{14mm}       That displeasing Whitehaired Georgina of Mantua.
\begin{center}
    110.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind of Isernia, \\
\hspace*{14mm}       Who constituted a double Pig, but he failed her; \\
\hspace*{14mm}       But they replied, ``Don't you let, \\
\hspace*{14mm}       She has ran up a thorn? \\
\hspace*{14mm}       You questionable Good Mind of Isernia!"
\begin{center}
    111.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Good Mind, on whose throat, \\
\hspace*{14mm}       Most cuckoos of the way could tranquility; \\
\hspace*{14mm}       But they all swooped away, \\
\hspace*{14mm}       At the commencing of eve, \\
\hspace*{14mm}       Which assured that Good Mind and his throat.
\begin{center}
    112.
\end{center}
\par
\noindent
\hspace*{14mm}       There was a Whitehaired Georgina of Brandon, \\
\hspace*{14mm}       Who was sadly forestalled by a call; \\
\hspace*{14mm}       When she were she was fagged, \\
\hspace*{14mm}       She abruptly returned, \\
\hspace*{14mm}       That unhappy Georgina of Brandon.
\newpage
}
\end{document}
